---
title: "Homework Problem 2"
author: "Dani Antos"
date: "September 24, 2017"
output: html_document
---
Loading the zombie.csv file from Prof Schmitt's GitHub
```{r echo=TRUE}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

#Question 1
Calculating population means and standard deviations is not the same as the sample mean and sd. This was part of Module 7. Wait, maybe the mean would be the same? It's just the variance and SD that are different?

Height:
```{r echo=TRUE}
mean(d$height)
h <- sum((d$height-mean(d$height))^2)/length(d$height)
sqrt(h)
```

Weight:
```{r echo=TRUE}
mean(d$weight)
w <- sum((d$weight-mean(d$weight))^2)/length(d$weight)
sqrt(w)
```

Age:
```{r echo=TRUE}
mean(d$age)
a <- sum((d$age-mean(d$age))^2)/length(d$age)
sqrt(a)
```

Number of zombied killed:
```{r}
mean(d$zombies_killed)
z <- sum((d$zombies_killed-mean(d$zombies_killed))^2)/length(d$zombies_killed)
sqrt(z)
```

Years of education:
```{r echo= TRUE}
mean(d$years_of_education)
e <- sum((d$years_of_education-mean(d$years_of_education))^2)/length(d$years_of_education)
sqrt(e)
```

#Question 2
Height:
```{r echo=TRUE}
library(ggplot2)
p <- ggplot(data=d, aes(x= gender, y= height))
p <- p +geom_boxplot()
p <- p + xlab("Gender") + ylab("Height")
p
```

Weight:
```{r echo=TRUE}
library(ggplot2)
m <- ggplot(data=d, aes(x= gender, y= weight))
m <- m +geom_boxplot()
m <- m + xlab("Gender") + ylab("Weight")
m
```

Age:
```{r echo=TRUE}
library(ggplot2)
q <- ggplot(data=d, aes(x= gender, y= age))
q <- q +geom_boxplot()
q <- q +xlab("Gender") + ylab("Age")
q
```

Number of zombies killed:
```{r echo=TRUE}
library(ggplot2)
b <- ggplot(data=d, aes(x= gender, y= zombies_killed))
b <- b +geom_boxplot()
b <- b + xlab("Gender") + ylab("Number of Zombies Killed")
b
```

Years of education:
```{r echo=TRUE}
library(ggplot2)
c <- ggplot(data=d, aes(x= gender, y= years_of_education))
c <- c +geom_boxplot()
c <- c + xlab("Gender") + ylab("Years of Education")
c
```

#Question 3
```{r}
library(ggplot2)
p <- ggplot(data=d, aes(x= age, y= height))
p <- p +xlab("Age") + ylab("Height")
p <- p + geom_point()
p
library(ggplot2)
q <- ggplot(data=d, aes(x= age, y= weight))
q <- q +xlab("Age") + ylab("Weight")
q <- q + geom_point()
q
```

Both height and weight seem to have a positive correlation with age. Height seems to have a stronger correlation with age than weight does just by looking at the two graphs.

#Question 4
Age:
```{r}
hist(d$age, breaks= seq(0, 40, 1), probability=TRUE, main="Histogram of Age", xlab="Age")
```

That gives me the histogram for the ages of the zombie survivors. 
```{r}
qqnorm(d$age, main= "Normal QQ Plot Age")
qqline(d$age, col="gray")
```

Age seems to follow a normal distribution.

Height:
```{r}
hist(d$height, breaks= seq(50, 90, 1), probability=TRUE, main="Histogram of Height", xlab="Height")
```

To be honest, I wasn't sure what to set the "by" argument as because each height is rounded to four decimal places but that histogram looked like a hot mess.
```{r}
qqnorm(d$age, main= "Normal QQ Plot Height")
qqline(d$age, col="gray")
```

Height also appears to follow a normal distribution.

Weight:
```{r}
hist(d$weight, breaks= seq(50, 250, 1), probability=TRUE, main="Histogram of Weight", xlab="Weight")
```
```{r}
qqnorm(d$weight, main="Normal QQ Plot Weight")
qqline(d$weight, col="gray")
```

Weight appears to follow a normal distribution. (Am I doing this right?)

Number of Zombies Killed:
```{r}
hist(d$zombies_killed, breaks= seq(0, 20, 1), probability = TRUE, main= "Histogram of Zombies Killed", xlab="Number of Zombies Killed")
```

This looks like a Poisson distribution, but I need to confirm that.
```{r}
p <- ppoints(length(d$zombies_killed))
head(p)
tail(p) #step one from module 8
theoretical_q<- qpois(ppoints(length(d$zombies_killed)), mean(d$zombies_killed)) #step 2 to get theoretical values
observed_q <- quantile(d$zombies_killed, ppoints(d$zombies_killed)) #step 3 to get quantiles of observed data
plot(theoretical_q, observed_q, main="Poisson QQ Plot Number of Zombies Killed", xlab="Theoretical Quantiles", ylab="Sample Quantiles")
```

Well that looks like a relatively straight line, but it looks much different than the other Q-Q plots, but I'd still say the Number of Zombies Killed follows a Poisson distribution, which I think also makes sense because we're counting. 

Years of Education:
```{r}
hist(d$years_of_education, breaks= seq(0, 10, 1), probability=TRUE, main= "Histogram of Years of Education", xlab="Years of Education")
```

Okay again I'm thinking Poisson, which would make sense again because we're counting.
```{r}
p <- ppoints(length(d$years_of_education))
head(p)
tail(p)
theoretical_q<- qpois(ppoints(length(d$years_of_education)), mean(d$years_of_education))
observed_q <- quantile(d$years_of_education, ppoints(d$years_of_education))
plot(theoretical_q, observed_q, main="Poisson QQ Plot Years of Education", xlab="Theoretical Quantiles", ylab="Sample Quantiles")
```

Again, it looks like a straight line but there are was fewer points than on the Q-Q plots for the normal distributions. But it looks like Years of Education follows a Poisson distribution.

#Question 5
```{r}
library(dplyr)
subset_1 <- sample_n(d, 30, replace=FALSE, weight=NULL, .env=NULL)
subset_1
```
So now that I'm working with a sample (rather than the whole population), I think that I can use the built in functions for mean and standard deviation. (I originally did the code in the order that the homework listed them, but rearranged them by variable because I thought it looked better) sample size=30

Age:
```{r}
m <- mean(subset_1$age)
m
s <- sd(subset_1$age)
s
error <- sd(subset_1$age)/sqrt(30)
error
#age has a normal distribution so I can use qnorm()
upper <- qnorm(0.975, mean=m, sd=s)
lower <- qnorm(0.025, mean=m, sd=s)
ci <- c(lower, upper)
ci
```

Height:
```{r}
m <- mean(subset_1$height)
m
s <- sd(subset_1$height)
s
error <- sd(subset_1$height)/sqrt(30)
error
#height has a normal distribution
upper <- qnorm(0.975, mean=m, sd=s)
lower <- qnorm(0.025, mean=m, sd=s)
ci <- c(lower, upper)
ci

```

Weight:
```{r}
m <-mean(subset_1$weight)
m
s <- sd(subset_1$weight)
s
error <- sd(subset_1$weight)/sqrt(30)
error
#weight has a normal distribution
upper <- qnorm(0.975, mean=m, sd=s)
lower <- qnorm(0.025, mean=m, sd=s)
ci <- c(lower, upper)
ci
```

Number of Zombies Killed: (I know that this is going to be different from the variables above because it follows a different distribution)
```{r}
m <- mean(subset_1$zombies_killed)
m
s <- sd(subset_1$zombies_killed)
s
error <- sd(subset_1$zombies_killed)/sqrt(30)
error
upper <- qpois(0.975, m)
lower <- qpois(0.025, m)
ci <- c(lower, upper)
ci #lower is 0, which makes sense to me because you can't kill negative zombies
```

Years of Education: (also Poisson distribution)
```{r}
m <- mean(subset_1$years_of_education)
m
s <- sd(subset_1$years_of_education)
error <- sd(subset_1$years_of_education)/sqrt(30)
error
upper <- qpois(0.975, m)
lower <- qpois(0.025, m)
ci <- c(lower, upper)
ci
```

#Question 6
Okay not gonna lie, I'm struggling a little bit conceptually here but I took notes on how you verbally explained this in class. So "subset of n" would be 30 because I want each subset to contain 30 rows, but I think I have to do each variable separately because r would try to take the mean of multiple variables and/or non-integer values. Then "x" would be 99 because we want to take subsets 99 times (for a total of 100 subsets including the one I created in **Question 5**).

So this is the code from Module 7:
set <- NULL 
n <- 15
for (i in 1:10000) {
    set[i] <- mean(sample(x, n, replace = TRUE)) }

and to my understanding, n=30, instead of 1:10000 it would be 1:99, and x would just be whatever variable I'm working with.
    

Age:    
```{r}
set <- NULL
n <- 30
for (i in 1:99) {
    set[i] <- mean(sample(d$age, n, replace = TRUE))
}
set
```
Okay, now to my understanding, this function's output will be 99 means of 30 ages each. I'm still a little unsure as to how to integrate this data with the last (100th) mean that I already computed. Also, wording is a bit confusing here, do you want me to take the mean of the 100 means? I guess that would make the most sense..
```{r}
v <- c(set, subset_1$age)
mean(v)
sd(v)
#sd is larger than error from question 5 which makes me think I did something wrong, but this sd is much smaller than the sd from number 5
hist(v, breaks= seq(10, 30, 1), probability=TRUE, main= "Histogram of Age Sampling Distribution", xlab="Age")
```

I guess it still looks normally distributed, the tails are longer than the previous histogram. I was expecting it to look more like a standard bell curve than the first histogram but now it makes sense for 19-21 to have the highest peaks, because any random subset of d for age would  be really really unlikely to have a mean as low as 15 or as high as 24.

Now I have to repeat for each variable and I'm finding it highly doubtful this is the easiest way to accomplish this task.

Height:
```{r}
set <- NULL
n <- 30
for (i in 1:99) {
    set[i] <- mean(sample(d$height, n, replace = TRUE))
}
set
v <- c(set, subset_1$height)
mean(v)
sd(v)
#again, sd is greater than the error calculated in question 5, but it is less than the sd calculated in question 5
hist(v, breaks= seq(50, 80, 1), probability=TRUE, main= "Histogram of Height Sampling Distribution", xlab="Height")
```

The histogram looks relatively normal. The right tail is definitely longer/larger than the left tail but I guess that could just mean that there are more shorter people than taller, so we'd be more likely to get a mean <70 (for example), but a mean of 70 or above would still be possible depending on the particular subset chosen. If that makes sense. It makes sense in my head.

Weight:
```{r}
set <- NULL
n <- 30
for (i in 1:99) {
    set[i] <- mean(sample(d$weight, n, replace = TRUE))
}
set
v <- c(set, subset_1$weight)
mean(v)
sd(v)
#sd here is greater than the error calculated in question 5, but less than the sd from question 5
hist(v, breaks= seq(70, 200, 1), probability=TRUE, main= "Histogram of Weight Sampling Distribution", xlab="Weight")
```

If you ignore the outliar at ~181, it looks like a pretty good bell curve. Which we expect because the other histogram also showed a normal distribution.

Number of Zombies Killed:
```{r}
set <- NULL
n <- 30
for (i in 1:99) {
    set[i] <- mean(sample(d$zombies_killed, n, replace = TRUE))
}
set
v <- c(set, subset_1$zombies_killed)
mean(v)
sd(v)
#sd here is greater than the error calculated in question 5, but less than the sd from question 5, also I don't really understand why we're comparing sd to se because they aren't the same
hist(v, breaks= seq(0, 10, 1), probability=TRUE, main= "Histogram of Number of Zombies Killed Sampling Distribution", xlab= "Number of Zombies Killed")
```

Wow this doesn't look like much to me, because I thought Poisson distribution would have a greater number of counts for 0 and 1, but maybe I can check this using a Q-Q plot?
```{r}
p <- ppoints(length(v))
head(p)
tail(p)
theoretical_q<- qpois(ppoints(length(v)), mean(v))
observed_q <- quantile(v, ppoints(v)) 
plot(theoretical_q, observed_q, main="Poisson QQ Plot Number of Zombies Killed Sampling Distribution", xlab="Theoretical Quantiles", ylab="Sample Quantiles")
```

I guess that looks straight-ish? Maybe the non-straightness is due to the peaks at 4-6 zombies killed (as seen in the histogram) instead of lower numbers, so it's not like the most perfect Poisson distribution ever.

Years of Education:
```{r}
set <- NULL
n <- 30
for (i in 1:99) {
    set[i] <- mean(sample(d$years_of_education, n, replace = TRUE))
}
set
v <- c(set, subset_1$years_of_education)
mean(v)
sd(v)
#sd is greater than error from question 5 but less than the sd from question 5, as expected
hist(v, breaks= seq(0, 8, 1), probability=TRUE, main= "Histogram of Years of Education Sampling Distribution", xlab= "Years of Education")
```

Like "zombies killed," years of education previously had a Poisson distribution. It still looks like a Poisson, but again, like the last histogram, the highest peaks aren't exactl where I would've expected them given an ideal Poisson distribution.

```{r}
p <- ppoints(length(v))
head(p)
tail(p)
theoretical_q<- qpois(ppoints(length(v)), mean(v))
observed_q <- quantile(v, ppoints(v))
plot(theoretical_q, observed_q, main="Poisson QQ Plot Years of Education Sampling Distribution", xlab="Theoretical Quantiles", ylab="Sample Quantiles")
```

I mean that looks pretty okay, again, I'm thinking that it's not completely straight because of where the highest peaks lie on the histogram. That's honestly just a guess though.